%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Martin Pettersson} % Your name
\address{+46706727003 \\ kontakt@martinpettersson.se} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{KTH Royal Institute of Technology}{2010-2015}{Computer Science}{Stockholm, Sweden}
\item MSE Degree Program in Computer Science and Technology
\end{rSubsection}

\begin{rSubsection}{Tohoku University}{2014-2015}{Computer Science, Natural Language Processing}{Sendai-shi, Miyagi, Japan}
\item Natural Science DEEP Program, Special Research Student, Graduate School of Information Sciences
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Nordita, Nordic Institute for Theoretical Physics} {September 2017 - March 2018}{Student Assistant}{Stockholm, Sweden}
\item Worked on OMDB, the Organic Materials Database, https://omdb.diracmaterials.org
\item Assisted in web development and similarity computations (machine learning),\\using mainly Python 3 and PHP with Laravel.
\end{rSubsection}

\begin{rSubsection}{Omegapoint AB}{September 2016 - August 2017}{Consultant, Software Developer}{Stockholm, Sweden}
\item Consulting jobs for clients within government and banking. 
\item Mostly Java backend development, but also some frontend and database related work.
\item First six months consisted of a tech-trainee program with a client case.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Digpro AB}{January 2016 - March 2016}{Software Developer}{Stockholm, Sweden}
\item Part-time Java programming with a geographical information system.
\item Attempted to replace an old Excel-library (JXL) to Apache POI in a very large code base.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Inui-Okazaki Communication Science Lab}{September 2014 - August 2015}{Research Student}{Sendai-shi, Miyagi, Japan}
\item I implemented a sentiment-level selectional preference model in Java using the Stanford NLP library.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{WeMind AB}{May 2013 - August 2014}{Web Developer}{Stockholm, Sweden}
\item My first part-time development job where I worked with Ruby, Ruby on Rails and PostgreSQL.
\item I maintained and developed a back-office system used in psychiatry.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & Java, Python, Javascript, C++, Ruby, C\# \\
Web & HTML, CSS, XML, Basics of PHP, REST, SOAP \\
Frameworks & Spring Boot, Ruby on Rails, Angular, React, .NET \\
Databases & MySQL, PostgreSQL, Oracle WCC, MS SQL Server \\
Tools & Git, SVN, Eclipse, IntelliJ, Visual Studio, VS Code, vim, Atom, Sublime \\
Operating Systems & Windows, OSX, Ubuntu, Linux Mint \\
Other & Maven, Gradle, IBM SPSS, IBM RAD, Agile Development, Scrum \\
3D Software & Autodesk Maya, Unity, Blender \\
Spoken Languages & Swedish (native), English (fluent), Norwegian (proficient) Japanese (basic) \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
