\title{Motivational Letter}
\documentclass[11pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac}
 
\newlfmP{dateskipbefore=10pt}
\newlfmP{sigsize=10pt}
\newlfmP{sigskipbefore=10pt}
 
\newlfmP{Headlinewd=0pt,Footlinewd=0pt}
 
 
\dateset{September 23, 2017}

\greetto{To Dr. Borysov and Dr. Geilhufe,}
\begin{document}
\begin{newlfm}
I have been a computer science student since 2010 and I studied here until 2014. During the academic year of 2014-2015 I participated in a one-year research training course at Tohoku University. I worked in the Inui-Okazaki Communication Science Lab where I learned the basics of NLP and Machine Learning. One of the bigger things I did there was to implement a sentiment-level selectional preference model to be used in a coreference resolution system. I worked mostly with Java (Stanford CoreNLP and the standard library) and Python (NLTK, scikit).

When I came home from Japan I decided to pause my studies and have since been working as a programming consultant for various companies in Stockholm. I have been mostly working with backend development in Java systems and with databases (PostgreSQL, Oracle databases, MySQL, and also some non-relational variants). I have also done some minor frontend work as well (notably Angular 2, but also some React).

I enjoy spending my spare time looking up popular open source projects, and I'm mostly interested in Python and C\# repos. I've also been doing a bunch of data-science and ML tutorials (like Tensorflow, Theano, some R-programming and other things).

Recently I decided to go back to school and finish off my degree here. I will be doing my final semester of courses (I'm taking Machine Learning, two ICT-courses, NLP and an old math course). After this I have the thesis job left and I would like to write it on some data-mining or ML-related topic.
 
I found a note in school regarding the job opportunity as part-time student assistant at Nordita. The position seems great for me since I have basic experience in all of the technologies you are mentioning, an interest in physics (my dream job would probably be to work on a physics/game engine) as well as being on the lookout for some part-time work where I can improve my skills.

Looking forward to hear from you.

Sincerely,

Martin Pettersson
\end{newlfm}
\end{document}